% MTConnect Specification and Material Statement:
\textbf{\color{mtc1}\Large {OPC Foundation and \mtconnect Institute}}

\begin{center}
    \textbf{AGREEMENT OF USE}
\end{center}

\textbf{COPYRIGHT RESTRICTIONS}

\begin{itemize}
    \item This document is provided "as is" by the OPC Foundation and the MTConnect Institute.
    \item Right of use for this specification is restricted to this specification and does not grant rights of use for referred documents.
    \item Right of use for this specification will be granted without cost.
    \item This document may be distributed through computer systems, printed or copied as long as the content remains unchanged and the document is not modified.
    \item OPC Foundation and the MTConnect Institute do not guarantee usability for any purpose and shall not be made liable for any case using the content of this document.
    \item The user of the document agrees to indemnify OPC Foundation and the MTConnect Institute and their officers, directors and agents harmless from all demands, claims, actions, losses, damages (including damages from personal injuries), costs and expenses (including attorneys' fees) which are in any way related to activities associated with its use of content from this specification.
    \item The document shall not be used in conjunction with company advertising, shall not be sold or licensed to any party.
    
    \item The intellectual property and copyright is solely owned by the OPC Foundation and the MTConnect Institute.
\end{itemize}

\textbf{PATENTS} 

The attention of adopters is directed to the possibility that compliance with or adoption of OPC or the MTConnect Institute specifications may require use of an invention covered by patent rights. OPC Foundation or the MTConnect Institute shall not be responsible for identifying patents for which a license may be required by any OPC or the MTConnect Institute specification, or for conducting legal inquiries into the legal validity or scope of those patents that are brought to its attention. OPC or the MTConnect Institute specifications are prospective and advisory only. Prospective users are responsible for protecting themselves against liability for infringement of patents.

\textbf{WARRANTY AND LIABILITY DISCLAIMERS}

WHILE THIS PUBLICATION IS BELIEVED TO BE ACCURATE, IT IS PROVIDED "AS IS" AND MAY CONTAIN ERRORS OR MISPRINTS. THE OPC FOUDATION NOR THE MTCONNECT INSTITUTE MAKES NO WARRANTY OF ANY KIND, EXPRESSED OR IMPLIED, WITH REGARD TO THIS PUBLICATION, INCLUDING BUT NOT LIMITED TO ANY WARRANTY OF TITLE OR OWNERSHIP, IMPLIED WARRANTY OF MERCHANTABILITY OR WARRANTY OF FITNESS FOR A PARTICULAR PURPOSE OR USE. IN NO EVENT SHALL THE OPC FOUNDATION NOR THE MTCONNECT INSTITUTE BE LIABLE FOR ERRORS CONTAINED HEREIN OR FOR DIRECT, INDIRECT, INCIDENTAL, SPECIAL, CONSEQUENTIAL, RELIANCE OR COVER DAMAGES, INCLUDING LOSS OF PROFITS, REVENUE, DATA OR USE, INCURRED BY ANY USER OR ANY THIRD PARTY IN CONNECTION WITH THE FURNISHING, PERFORMANCE, OR USE OF THIS MATERIAL, EVEN IF ADVISED OF THE POSSIBILITY OF SUCH DAMAGES.

The entire risk as to the quality and performance of software developed using this specification is borne by you. 

\textbf{RESTRICTED RIGHTS LEGEND}

This Specification is provided with Restricted Rights. Use, duplication or disclosure by the U.S. government is subject to restrictions as set forth in (a) this Agreement pursuant to DFARs 227.7202-3(a); (b) subparagraph (c)(1)(i) of the Rights in Technical Data and Computer Software clause at DFARs 252.227-7013; or (c) the Commercial Computer Software Restricted Rights clause at FAR 52.227-19 subdivision (c)(1) and (2), as applicable. Contractor / manufacturer are the OPC Foundation, 16101 N. 82nd Street, Suite 3B, Scottsdale, AZ, 85260-1830

\textbf{COMPLIANCE}

The combination of the MTConnect Institute and OPC Foundation shall at all times be the sole entities that may authorize developers, suppliers and sellers of hardware and software to use certification marks, trademarks or other special designations to indicate compliance with these materials as specified within this document. Products developed using this specification may claim compliance or conformance with this specification if and only if the software satisfactorily meets the certification requirements set by the MTConnect Institute or the OPC Foundation. Products that do not meet these requirements may claim only that the product was based on this specification and must not claim compliance or conformance with this specification. 

\textbf{TRADEMARKS}

Most computer and software brand names have trademarks or registered trademarks. The individual trademarks have not been listed here.

\textbf{GENERAL PROVISIONS}

Should any provision of this Agreement be held to be void, invalid, unenforceable or illegal by a court, the validity and enforceability of the other provisions shall not be affected thereby. 

This Agreement shall be governed by and construed under the laws of Germany.

This Agreement embodies the entire understanding between the parties with respect to, and supersedes any prior understanding or agreement (oral or written) relating to, this specification.


\clearpage
