

%% OPC UA Terms

\newglossaryentry{Node}
{
  type=opc,
  name = {Node},
  description = {The elements of the UA model are represented in the AddressSpace as Nodes. Each Node is assigned to a NodeClass and each NodeClass represents a different element of the Object Model.}
}

\newglossaryentry{DataType}
{
  type=opc,
  name = {DataType},
  description = {instance of a DataType Node that is used together with the ValueRank Attribute to define the data type of a Variable}
}

\newglossaryentry{TargetNode}
{
  type=opc,
  name = {TargetNode},
  description = {a Node that is referenced by another Node}
}

\newglossaryentry{TypeDefinitionNode}
{
  type=opc,
  name = {TypeDefinitionNode},
  description = {Node that is used to define the type of another Node}
}


\newglossaryentry{InstanceDeclaration}
{
  type=opc,
  name = {InstanceDeclaration},
  description = {Node that is used by a complex \gls{TypeDefinitionNode} to expose its complex structure}
}

\newglossaryentry{ModellingRule}
{
  type=opc,
  name = {ModellingRule},
  description = {metadata of an InstanceDeclaration that defines how the \gls{InstanceDeclaration} will be used for instantiation and also defines subtyping rules for an \gls{InstanceDeclaration}}
}

\newglossaryentry{TypeDefinition}
{
  type=opc,
  name = {TypeDefinition},
  description = {The creation of an OPC UA Type}
}

\newglossaryentry{Variable}
{
  type=opc,
  name = {Variable},
  description = {}
}

\longnewglossaryentry{ValueRank}
{
  type=opc,
  name = {ValueRank}%,
%  description = {This Attribute indicates whether the Value Attribute of the Variable is an array and how many dimensions the array has.}
}
{
  This Attribute indicates whether the Value Attribute of the Variable is an array and how many dimensions the array has. It may have the following values:
  \begin{itemize}
    \item n > 1: the Value is an array with the specified number of dimensions.
    
    \item OneDimension (1): The value is an array with one dimension.
    \item OneOrMoreDimensions (0): The value is an array with one or more dimensions.
    \item Scalar (-1): The value is not an array.
    \item Any (-2): The value can be a scalar or an array with any number of dimensions.
    \item ScalarOrOneDimension (-3): The value can be a scalar or a one dimensional array.
  \end{itemize}
  All DataTypes are considered to be scalar, even if they have array-like semantics like ByteString and String.
}

\newglossaryentry{NodeClass}
{
  type=opc,
  name=NodeClass,
  plural=NodeClasses,
  description = {The NodeClasses defined to represent Objects fall into three categories: those used to define instances, those used to define types for those instances and those used to define data types}
}

%% MTConnect Terms

\newglossaryentry{Agent}
{
  type=mtc,
  name = {Agent},
  description = {The Middleware Broker and Protocol Server for the MTConnect Standard using a REST HTTP Interface}
}

\newglossaryentry{MTComponent}
{
  type=mtc,
  name = Component,
  description = {A functional unit of a piece of manufacturing equipment}
}

\newglossaryentry{MTDataItem}
{
  type=mtc,
  name = DataItem,
  description = {A piece of information regarding the state, event, or continuous variable related to a \gls{MTComponent} semantically identified by the \texttt{type} and \texttt{subType}}
}

\newglossaryentry{Adaper}
{
  type=mtc,
  name=Adapter,
  description = {An application that provides data from a piece of equipment to an MTConnect Agent}
}

\newglossaryentry{ControlledVocab}
{
  type=mtc,
  name={Controlled Vocabulary},
  plural = {Controlled Vocabularies},
  description = {A restricted set of values that may be published as the Valid Data Value for a Data Entity.}
}

\newglossaryentry{SampleRequest}
{
  type=mtc,
  name={Sample Request},
  description = {A request from the MTConnect \gls{Agent} for a stream of time series data.}
}

\newglossaryentry{DataItemType}
{
  type=mtc,
  name={DataItem type},
  description = {The top level taxonomy classification of \glspl{DataItem}}
}

\newglossaryentry{PascalCase}
{
  type=mtc,
  name={Pascal Case},
  description = {The first letter of each word is capitalized and the remaining letters are in lowercase. All space is removed between letters}
}

\newglossaryentry{LowerCamelCase}
{
  type=mtc,
  name={Lower Camel Case},
  description={the first word is lowercase and the remaining words are capitalized and all spaces between words are removed.}
}

%%% Local Variables:
%%% mode: latex
%%% TeX-master: "main"
%%% End:
