The \mtterm{Condition} \mtterm{DataItem} \mtterm{category} in MTConnect is the mechanism for reporting alarms on the machine classified by type and subType--such as an overload of a motor or high temperature or a collection of system level warnings or faults.

The earlier \mtterm{Alarm} \mtterm{Event} facility changed to a more state-based architecture where the \mtterm{Condition} was in one of the following three states: Normal – everything is fine, Warning – something is going wrong, but may self-correct, to Fault – a failure that needs manual attention. The change was to address the semantic classification of \mtterm{Alarms} and remove ambiguity about the \mtterm{Alarm} severity.

The Condition model is different from the Event model for a lot of the same reasons OPC has the \uaterm{ConditionType} as \uaterm{Object} and as an \uaterm{Event}. In UA, the \uaterm{Object} in the address space keeps the state of the condition, whereas the individual \uaterm{Alarms} are discrete events.

In MTConnect, the \mtterm{Condition} keeps the active state as well. In streaming (\mtterm{sample}) request, the \mtterm{Conditions} like an event stream. With a \mtterm{current} request, all active conditions are reported, even if there are multiple active conditions for a given type. Usually, an \mtterm{Event} can only have one value at a time, MTConnect \mtterm{Condition} is different and can have multiple values, as in the case where there are multiple system alarms for a component or a syntax errors in a part program.

The Condition uses the attribute \xmlattribute{nativeCode} as you use the BranchId in the UA Condition. Each unique \xmlattribute{nativeCode} is consider another activation of the Condition. Only when a \mtterm{Normal} with no \xmlattribute{nativeCode} cleared all active Conditions, or each are cleared separately (going back to a Normal state), does the condition report Normal when for a \mtterm{current} request.

\mtterm{Condition} provides a stateful way of managing \mtterm{Alarms} in a similar way to OPC UA, but since we are not addressing the requirements of an interactive model (we are read-only), we are only reporting on the states of the conditions. 

The documentation for the condition behavior in MTConnect can be found in Section 5.7 and 5.8 of \cite{MTCPart3} and an overview in \cite{MTCPart2}.

The MTConnect Data Item with Category of \texttt{CONDITION} are mapped to the OPC UA \uaterm{ConditionType}s  in \cite{UAPart9} with a \uaterm{TwoStateVariableType} that represents the current state of all the active \uaterm{branches} of this \mtterm{Condition}.